### 2016-07-13 version0.0/intro0.0.tex
finishing edits on intro

\section{Prelude}
\label{sec: overview}
%what do we have inside galaxies:
% stuff we don't care about because they don't have a big contribution on the SED 1) planets; 2) black holes 3) dark matter
Inside every galaxy, there are millions of stars, planets, and black holes, as well as dust and gas, which all affect each others' formation, evolution and extinction.
There is also dark matter inside every galaxy, which to the best of our knowledge only has gravitational effects on the other components.
Nearly all the information we can obtain from galaxies other than our own comes from their light. % now we can detect gravitational wave which is not part of the SEDs, right? % PB: right.
Young and evolved stars and dust and gas in the space between the stars are the most important contributors to the spectral energy distributions (SEDs) of galaxies. %PB: explain what you mean by spectral energy distribution
We cannot detect any contribution from planets and black holes to SEDs due to their low intensity compared to these other components. %or the limitation of our detectors. % PB: need to rephase a bit  to mention AGN!
Therefore, with properly modeling observed features in SEDs we can extract information about the evolution of stars, dust and gas inside galaxies.

@@

%ISM 1)Gas 2)dust
There could be a galaxy without stars (i.e. dark galaxies~\citep[][and references therein]{Cantalupo12}), but there will never be a galaxy without gas. %PB: this is a very strong statement. Some galaxies, like dwarf ellipticals, are pretty gas-free (at least now). So qualify this a bit.
Gas and dust in galaxies can be found in the space between stars that is called the interstellar medium (ISM). The ISM is full of low density gaseous clouds with neutral or ionized atoms and/or molecules, and microscopic dust grains.
The gas and dust in the ISM are heated by interstellar radiation field and cool through a variety of line and continuum processes which usually depend on the local physical conditions. 
The effect of the ISM on stellar formation is undeniable;  it provides the raw material for the formation of stars~\citep[e.g.][]{Kennicutt08,Bigiel08}.
Studying the interstellar medium is not only essential for understanding of the formation of stars, but also it is necessary for interpretation of stellar evolution in that stars release their material into the ISM when they reach the end of their evolution.

% Metallicity %PB: you start talking about metallicity but then switch over to SF. Overview the SF process first, then talk about how metallicity affects it.
Metallicity, which is defined as the ratio of abundance of metals to the abundance of hydrogen, affects formation and evolution of stars indisputably. %PB: define what "metals" means here
In a galaxy like our own, star formation begins with the condensation of giant molecular clouds (GMCs, $\sim 10^7$ M$_{\odot})$ in the ISM due to gravitational instabilities. 
The interplay of turbulence and magnetic fields with self-gravity is believed to be responsible for the formation of clumps within GMCs. 
Some of these clumps develop into self-gravitating cores, which have a similar distribution to stellar initial mass function (IMF) while turbulence and magnetic fields play central roles in defining this distribution (see~\cite{McKee07} for more detail). %PB: this sentence has a lot of concepts in it: going to be hard for non-astronomer to understand
\cite{Walch11} showed that in the case of large scale turbulence, the effect of metallicity on star formation is negligible, but if turbulence is decaying,  metallicity has a strong impact on stabilizing self-gravitating cores. %PB: please check edits to prev sentence
Metals also play an important role in heating, cooling and ionizing processes in the ISM. %%ADD ref.
Since cooling is one of the main reasons for condensation of GMCs~\citep[e.g.][]{Maio07}, in low metallicity regions star formation may be suppressed. %Sahar: should I talk about metallicity in stars and their relation with age? %PB: yes. Need to introduce the general idea of chemical evolution - you hint at this above, but can state it explicitly.

%what does SED look like?
Our primary source of information for galaxies, specifically unresolved ones, is their spectral energy distributions. %PB: since SED is a really important concept, I took out the acronym here.
Broadly speaking, young and hot stars emit most of their light in iltraviolet (UV) wavelengths, evolved stellar populations show themselves in optical and near-infrared (NIR) emission, and gas and dust heated by stellar emission are bright in mid-infrared (MIR) or far-infrared (FIR) wavelengths.
Therefore, UV-to-IR SEDs contain valuable information about galaxies' stellar evolution and their ISM. 
Other wavelengths regimes in galaxy SEDs (i.e. X--ray, radio), that are dominated by processes such as active galactic nuclei, quasars, and supernovae shocks, are beyond the scope of this thesis.
The general shape of SEDs mirrors the morphological type of galaxies; starburst galaxies, which have high star formation rates (SFRs), emit the bulk of their energy in the UV, while the light of quiescent galaxies is dominated by optical and IR emission. 
Detailed information about the age of stellar populations and other properties of galaxies can be determined by modelling their SEDs.

 %how do you model it? %SED model CIGALE %Population synthesis ----> SFR, stellar mass %PB: Need more detail here - how do SED models include SFR, Mstar, etc?
The stellar population synthesis method, which sums stellar spectra of a galaxy to produces its spectrum, has been widely utilized since the 1970s~\citep[e.g.][]{Tinsley72,Searle73} to model SEDs of galaxies.
A through SED model must include stellar population models~\citep[e.g.][]{Bruzual93,Bruzual03,Maraston05}, stellar emission and dust attenuation~\citep[e.g.][]{Calzetti00,Dopita05}, dust grain emission such as from polycyclic aromatic hydrocarbons~\citep[PAHs; e.g.][and references therein]{Tielens08}, and IR emission from gas and dust~\citep[e.g.][]{Chary01,Dale02,Lagache03,Lagache04,Smith07a,Draine07}.%, to fit the observed SEDs.
Many groups have modelled SEDs for different types of galaxies and created SED templates (for more information see the review of \cite{Walcher11} on fitting of SEDs and references therein).
Since the physical parameters of templates generated by the SED models are known, we can find properties of observed galaxies by fitting their SEDs using the templates.
One example of an SED-fitting code is {\em CIGALE}: Code Investigating GALaxy Emission~\citep{Noll09}.
It combines SED models to find the best-fit SED for observed data in the rest-frame UV-to-IR and finds physical properties of galaxies such as SFR, stellar mass and dust attenuation.

%PB: I think you need a one-or-two sentence intro to the overall thesis goals here, so that the reader can see why you are talking about all of this stuff.
In this chapter, we present a review of observational methods of measuring the star formation rate and the main properties that affect measuring and scaling the SFR. A discussion of the ISM and its role in star formation is presented in $\S$~\ref{sec: ism_intro}. In $\S$~\ref{sec: sfr_intro} we discuss measuring the star formation rate, followed by a discussion of the measurement of the stellar mass in $\S$~\ref{sec: starmass_intro}. Current issues about star formation and its relation to other properties of a galaxy are discussed in $\S$~\ref{sec: pre_intro}.

@@

\section{Interstellar Medium} %PB: suggest "Components of the Interstellar Medium in Galaxies" or "The Interstellar Medium in Galaxies"
\label{sec: ism_intro}
%how do we observe it
%what the observation tell us
% how do we measure the dust and gas
The interstellar medium in galaxies is a complex system with a wide range of structures, but these structures can be divided into two main components: gas and dust. %PB: in general, don't start a sentence with an acronym.
The gas in the ISM of galaxies is mostly made of hydrogen and helium with 1 per cent heavier elements (metals), and can be in the form of clouds or diffuse regions.
Gas clouds include molecular clouds, cold neutral atomic hydrogen (\hi) or hot \hi~clouds, and diffuse gas can be either \hii~(ionized hydrogen) regions or hot intercloud medium.
Dust mostly contains silicate, graphite grains can be seen in dark clouds or galactic cirrus.
%Among these regions in ISM, molecular clouds, \hii~regions and dust clouds have important role in understanding star formation in galaxies. 
Emission lines from atoms or ions (i.e \hii~regions) in a hot gas, lines from molecules in cold clouds and 21~cm emission of \hi~are the main observational signatures of the gas in the ISM of galaxies.
Dust can be observed directly through far-infrared and sub-millimeter wavelength emission or indirectly through its extinction and attenuation effects (see Sec.~\ref{sec: extinction}).

Molecular clouds in the ISM are cold ($\sim10$ K) and dense ($ 50<n<500$ cm$^{-3}$); masses of molecular clouds range from a few to millions of solar masses. %~\citep{Bolato08}. %PB: why no citation?
Density in the molecular clouds is not uniform; dense and colds clumps. %PB: I don't get this sentence.
Since these clumps are ideal places to form stars, studying molecular clouds has an important role in understanding formation of stars
However, H$_2$ molecules, the main component of molecular clouds, have no permanent electric dipole moment which makes them difficult to detect in visible light. %PB: just visible light, or all wavelengths?
The second dominant component, helium, is a mono-atomic gas and has the same problem as hydrogen, but these clouds also contain heavier elements such as carbon monoxide, hydrogen cyanide, water, ammonia and more than tens of others.
Carbon monoxide (CO) molecules are the third-most abundant constituent of molecular clouds.
In fact, most of our knowledge from extragalactic molecular clouds comes from observing line emission of CO molecules, which {\bf due to their heavy weight, they have very low rotational state} and can be excited in the temperature of molecular clouds. %PB just extragalactic, or Galactic too? Phrase marked with \bf needs clarification
Other heavier molecules have emission lines which are also detectable in the spectrum of clouds (specially galactic ones), but observing CO emission is the most common way to study the properties of molecular clouds i.e. their mass (see Sec.~\ref{sec: ismmap} for more details).

@@

\hii~regions are hot and low density regions that are mostly located in the disks of spiral galaxies.
High energy UV photons emitted by massive new born stars have sufficient energy to ionize their surrounding gas, and
~\halpha emission is the main observational feature of \hii~regions.
The temperature and density of these regions can be estimated by observing other recombination lines such as H$\beta$, \sii, \oii, \oiii, and \nii. 
Optically bright \halpha emission from \hii~regions correlates with number of new massive stars in regions and can be used as a star formation tracer~\citep[e.g.][]{Kennicutt98b,Calzetti13}. %PB: moved this sentence.
Studying \hii~regions provides valuable insight into star forming regions by providing information such as star formation rate, initial mass function (IMF), and distribution of ionizing stellar masses~\citep[][and references therein]{Azimlu11}.

%PB: it is difficult to see how the sentences in this paragraph fit together. Right now it reads like a collection of barely-related facts.
Dust has an insignificant effect on the mass of the ISM, but it plays crucial roles in the ISM's evolution.
The total gas mass of galaxies can be determined using optical depth in sub-mm waveband of dust emission. 
In spiral galaxies dust grains are located in cold regions ($\sim 30$~K) and have a power-law distribution of size.
Source of dust thermal emission is from stars and shape of the continuum depends on size of the grain.
Mid-infrared emission from dust grains is mainly dominated by PAHs heated by evolved stellar population~\cite{Smith07a} or recently formed type ``A" and ``B'' stars~\cite{Peeters04}. %PB: A and B or O and B?
Large grains that are either heated by light from star-forming regions or by the interstellar radiation field from total stellar population emit most of their light in far-infrared~\citep[e.g.][]{Calapa14, lu14}
Dust is the main source of extinction and reddening of starlight (See Sec.\ref{sec: extinction} for more information).

\subsection{Map of ISM} %PB: suggest "Mapping the Interstellar Medium"
\label{sec: ismmap}
Measuring the mass of gas in galaxies is a necessary step to know how much raw material is available for forming stars.
A map of the total gas mass in the ISM can be produced by direct observations of gas or using interstellar dust as a tracer. 
Neutral atomic and molecular hydrogen are the most common components of the ISM. %PB: same element
Therefore, to produce a total gas mass map in galaxies, maps of these two components can be added together and multiplied by a constant factor to account for heavier elements which are mostly He. %PB: point out that He can't be observed directly
Another way to do the mapping is to assume that the ratio of total gas to dust is constant across the galaxy, and convert dust observations to a map of total gas mass.

@@

The surface density of gas in the ISM of galaxies can be measured by direct observation of the neutral and molecular hydrogen.
This method can be promising provided that the spatial resolution of observational data is high enough, although due to technical limitations, attaining enough spatial resolution to resolve clouds is almost impossible. This problem shows itself for distant galaxies more than nearby galaxies. 
As a result, using this method is limited and has a lot of uncertainties. % PB last 3 sentences are vague. What exactly ar the limitations and uncertainties?

@@

\cite{Young91} described the relationship between the CO luminosity of a cloud and its mass. The CO luminosity of a cloud is:
\begin{equation}
L_{CO} = D^2 \int I_{\rm CO} d\Omega 
\end{equation}
where $D$ is the distance to the cloud and 
$I_{\rm CO}$ is the CO brightness temperature integrated over the line profile.
It can be written as ${\int T_{\rm CO} dV}$ where $T_{\rm CO}$ is the peak brightness temperature in the CO line and $V$ is the line-width. %PB units for these quantities?
For a uniform cloud with a radius $R$, the CO luminosity is given by:
 \begin{equation}
L_{\rm CO} = \pi R^2 T_{\rm CO} \Delta V
\end{equation}

Galactic molecular clouds are self-gravitating systems. %PB: ref?
Thus, using the virial theorem leads to calculating the mass of the cloud: %(PB note: "Virial" is not a name, no capital needed)
 \begin{equation}
 \label{equ: vir}
 M_{cloud} = L_{\rm CO} \sqrt{\frac{4\rho}{3\pi G T_{\rm CO}}}
 \end{equation}
 where $\sqrt{\frac{4\rho}{3\pi G T_{\rm CO}}}$ is called the conversion factor. %PB: what is \rho here?
 Equation~\ref{equ: vir} shows that the total mass of molecular clouds and the total CO luminosity of a galaxy are directly related~\citep{Young91}. % PB: you refer to individual clouds above, then you jump to totals for the galaxy.  Is this OK to do? (what assumption about optical depth is being made?)
 The relation between CO emission and H$_2$ cloud mass is shown as
%PB: no paragaph break between the text and the beginning of the equation
\begin{equation}
N_{\rm H_2}/\rm cm^{-2} = X_{\rm CO} \times I_{\rm CO}/{\rm K km s}^{-1}
\end{equation}
where X$_{\rm CO}$ is the conversion factor (also known as the X-factor).
The X-factor is different in each galaxy and sometimes is even different in regions within a galaxy due to differences in properties such as metallicity. 
Though assuming a constant conversion factor for galaxies like M82 and M31 can lead to accurate estimation of global molecular gas mass, in regions with low metallicity there are uncertainties. %PB: need references here
Various groups are working on observations of different types of galaxies to measure the X-factor for them~\citep{Wilson95, Bosselli02, Bolato13}.

In order to empirically determine the relation between H$_2$ masses and CO luminosities, many observational attempts have been made on both Galactic and extragalactic scales. 
One of the most significant studies in this regard was done by~\cite{Solomon87}, who studied this relation over more than 273 clouds inside the Milky Way and found a strong correlation between the virial mass of molecular clouds and CO luminosity. 
In Local Group galaxies, several groups have measured size, line width, and CO luminosity of molecular clouds and investigated the relation between  their virial masses and CO emission in environment other than the Milky Way. However, extragalactic investigations were limited to nearby galaxies due to technical problems regarding resolution and sensitivity of the telescopes. 
To measure the clouds in distant galaxies, spatial resolution of maps must be better than 40 pc which is the typical size of a giant molecular cloud~\citep[e.g.][and refrences therein]{Bolato13}. %PB: put these last 2 sentences at end of paragraph
%PB no new paragraph here
Pioneering works in measuring the extragalactic conversion factor were done for M31 and M32~\citep[e.g.,][]{Wilson89, Wilson90}. 
Fig.~\ref{fig: mco} shows the CO luminosity verses virial masses of molecular clouds in the Milky Way, M31, M33, and IC~10. 
The extragalactic molecular clouds are similar to those in the Milky Way. 
The conversion between the CO luminosity and H$_2$ masses is still a controversial topic~\citep[e.g.][]{Narayanan11, Bolato13, Sandstrom13}.
Problems regarding metallicity are not yet solved and it is still not clear whether the conversion factor is global or local.

\begin{figure}
\label{fig: mco}
\centering
\includegraphics[width=16cm]{../image_intro/mvirial_lco.eps}
\caption{Relation between the virial mass and CO luminosity for the Milky Way (dots), M33 (open circles), M31 (triangles), and IC~10 (squares) clouds. Virial masses are measured from selected high spatial resolution CO observations. The extragalactic molecular clouds are very similar to those in the Milky Way. Adapted from~\cite{Young91}.}
\end{figure}

%\subsubsection{Neutral Gas} %PB: paragraph needs a topic sentence
The density of the atomic hydrogen along the line-of-sight is proportional to the intensity of the 21-cm emission. %PB: reverse: intensity of 21cm is proportional to density. Is this optically thin/thick ?
Atomic hydrogen along the line-of-sight contributes to the energy received. %PB does this sentence add something to the previous one?
These properties make the 21-cm line a very useful tool to study gas in the ISM and trace the large-scale distribution of galaxies in the universe (\hi is detectable in most spiral galaxies and some elliptical galaxies).
Although the 21-cm emission is the most reliable technique to map the ISM, the linear relationship between the intensity and the column density of the gas breaks down when the gas is optically thick~\citep{Braun09}. %PB: do you want to give the equation for converting between intensity and mass for HI, the way you did for CO?

@@

Studying the gas clouds in the ISM of distant galaxies by using direct methods is almost impossible and not practical. %PB: why?
\cite{Hildebran83} was the first to suggest that one way to estimate the mass of the gas in the ISM might be from the optical depth of the sub-mm continuum emission from the dust; continuum dust emission is generally optically thin. 
The Herschel Space Telescope \cite{Pilbratt10} measured the continuum dust emission from hundreds of galaxies\citep{Eales10, Oliver12}. 
This amount of observational data provides a unique opportunity to study the ISM of galaxies using dust emission. 
%PB: join these 2 paragraphs
One of the advantages of using the dust emission as a tracer of the gas mass is that unlike the direct method, high spatial resolution is not necessary. %PB: why?
The other important advantage is that this method solves the newly-found problem of the ``dark gas" in galaxies. 
Dark gas is a significant fraction of gas in galaxies which is traced by neither 21-cm emission nor CO emission~\citep{Abdo10}. 
As such it is very difficult to detect with telescopes, but an accurate gas to dust ratio can lead to an accurate estimate of dark gas mass in galaxies.

>>>>

\section{Prelude}
\label{sec: overview}
%what do we have inside galaxies:
% stuff we don't care about because they don't have a big contribution on the SED 1) planets; 2) black holes 3) dark matter
Inside every galaxy, there are millions of stars, planets, and black holes, as well as dust and gas, which all affect each others' formation, evolution and extinction.
There is also dark matter inside every galaxy, which to the best of our knowledge only has gravitational effects on the other components.
Nearly all the information we can obtain from galaxies other than our own comes from their light.
Since each observational phenomenon inside galaxies emits most of its energy in specific wavelengths, 
a plot of brightness/flux density of galaxies as a function of wavelengths, which is called spectral energy distribution (SED), is a useful tool to have a intuition about galaxies. 
Young and evolved stars, dust and gas in the space between the stars are the most important contributors to the spectral energy distributions (SEDs) of galaxies.
We cannot detect any contribution from planets and black holes, the ones without accretion disc, to SEDs due to their low intensity compared to these other components.
Therefore, with properly modeling observed features in SEDs we can extract information about the evolution of stars, dust and gas inside galaxies.

@@

%ISM 1)Gas 2)dust
%There could be a galaxy without stars (i.e. dark galaxies~\citep[][and references therein]{Cantalupo12}), but there will never be a galaxy without gas. %: this is a very strong statement. Some galaxies, like dwarf ellipticals, are pretty gas-free (at least now). So qualify this a bit. done
Among observable objects in galaxies, gas has a crucial role in formation and evolution of galaxies.
Gas and dust in galaxies can be found in the space between stars that is called the interstellar medium (ISM). The ISM is full of low density gaseous clouds with neutral or ionized atoms and/or molecules, and microscopic dust grains.
The gas and dust in the ISM are heated by interstellar radiation field and cool through a variety of line and continuum processes which usually depend on the local physical conditions. 
The effect of the ISM on stellar formation is undeniable;  it provides the raw material for the formation of stars~\citep[e.g.][]{Kennicutt08,Bigiel08}.
Studying the interstellar medium is not only essential for understanding of the formation of stars, but also it is necessary for interpretation of stellar evolution in that stars release their material into the ISM when they reach the end of their evolution.

In a galaxy like our own, star formation begins with the condensation of giant molecular clouds (GMCs, $\sim 10^7$ M$_{\odot})$ in the ISM due to gravitational instabilities. 
The denser regions within GMCs collapse under their own gravity, self-gravity, and creates clumps.
Some of these clumps develop into self-gravitating cores, which have a similar distribution to stellar initial mass function (IMF).
Then these clumps continue to become denser and transfer to protostars. 
Since the protostars have higher mass than their surrounding, more gas from GMCs add to protostars.
This procedure continues until hydrogen burning in centre of protostars starts (see~\cite{McKee07} for more detail).

Metallicity, which is defined as the ratio of abundance of metals (any element heavier than hydrogen and helium) to the abundance of hydrogen, affects formation and evolution of stars indisputably.
\cite{Walch11} showed that in the case of large scale turbulence, the effect of metallicity on star formation is negligible, but if turbulence is decaying,  metallicity has a strong impact on stabilizing self-gravitating cores.
Metals also play an important role in heating, cooling and ionizing processes in the ISM.
Since cooling is one of the main reasons for condensation of GMCs~\citep[e.g.][]{Maio07}, in low metallicity regions star formation may be suppressed. 
Amount of metals in stars affect their evolutionary tracks~\citep[e.g.][and references therein]{Maeder02}.
For example, low metallicity stars tend to be have lower mass loss by stellar wind than that with higher metallicity.
Since there is lower amount of mass loss in low metallicity stars, hence no loosing angular momentum because of wind, massive low metallicity stars rotate faster.
Being more massive at the end of evolutionary track, makes massive low metallicity stars lower chance to explode (become a supernova).

%what does SED look like?
Our primary source of information for galaxies, specifically unresolved ones, is their spectral energy distributions. 
Broadly speaking, young and hot stars emit most of their light in ultraviolet (UV) wavelengths, evolved stellar populations show themselves in optical and near-infrared (NIR) emission, and gas and dust heated by stellar emission are bright in mid-infrared (MIR) or far-infrared (FIR) wavelengths.
Therefore, UV-to-IR SEDs contain valuable information about galaxies' stellar evolution and their ISM. 
Other wavelengths regimes in galaxy SEDs (i.e. X--ray, radio), that are dominated by processes such as active galactic nuclei, quasars, and supernovae shocks, are beyond the scope of this thesis.
The general shape of SEDs mirrors the morphological type of galaxies; starburst galaxies, which have high star formation rates (SFRs), emit the bulk of their energy in the UV, while the light of quiescent galaxies is dominated by optical and IR emission. 
Detailed information about the age of stellar populations and other properties of galaxies can be determined by modelling their SEDs.

 %how do you model it? %SED model CIGALE %Population synthesis ----> SFR, stellar mass 
The stellar population synthesis method, which sums stellar spectra of a galaxy to produces its spectrum, has been widely utilized since the 1970s~\citep[e.g.][]{Tinsley72,Searle73} to model SEDs of galaxies.
A through SED model must include stellar population models~\citep[e.g.][]{Bruzual93,Bruzual03,Maraston05}, stellar emission and dust attenuation~\citep[e.g.][]{Calzetti00,Dopita05}, dust grain emission such as from polycyclic aromatic hydrocarbons~\citep[PAHs; e.g.][and references therein]{Tielens08}, and IR emission from gas and dust~\citep[e.g.][]{Chary01,Dale02,Lagache03,Lagache04,Smith07a,Draine07}.
Many groups have modelled SEDs for different types of galaxies and created SED templates (for more information see the review of \cite{Walcher11} on fitting of SEDs and references therein).
Since the physical parameters of templates generated by the SED models are known, we can find properties of observed galaxies by fitting their SEDs, (either by minizing $\chi^2$ or by Bayesian analysis)  using the templates.
One example of an SED-fitting code is {\em CIGALE}: Code Investigating GALaxy Emission~\citep{Noll09}.
It combines SED models and uses Bayesian analysis to find the best-fit SED for observed data in the rest-frame UV-to-IR.
Some of the physical properties of galaxies should be assumed as an input data to find best SED, and others will be derived from SED results~\citep[See][for more detail]{Walcher08}.
For example, the Best fitted SED has information regarding star formation history and stellar mass to light ratio.
By integrating star formation history over specific time scale, SFR can be derived. 
knowing the stellar mass to light ratio, one can used observed luminosity to calculate stellar mass in galaxies.

Formation of stars in galaxies depends on many parameters, gas, stellar mass, metallicity, dust, galaxy's morphology and location of the star forming region inside the galaxy.
In extragalactic astronomy, measuring the rate that stars form is uncertain and relies upon theoretical models and observational data.
Studying star formation and its relation to other quantities in galaxies in an ongoing progress.
In this chapter, we present a review of observational methods of measuring the star formation rate and the main properties that affect measuring and scaling the SFR. A discussion of the ISM and its role in star formation is presented in $\S$~\ref{sec: ism_intro}. In $\S$~\ref{sec: sfr_intro} we discuss measuring the star formation rate, followed by a discussion of the measurement of the stellar mass in $\S$~\ref{sec: starmass_intro}. Current issues about star formation and its relation to other properties of a galaxy are discussed in $\S$~\ref{sec: pre_intro}.

@@

\section{Components of the Interstellar Medium} 
\label{sec: ism_intro}
%how do we observe it
%what the observation tell us
% how do we measure the dust and gas
The interstellar medium in galaxies is a complex system with a wide range of structures, but these structures can be divided into two main components: gas and dust.
The gas in the ISM of galaxies is mostly made of hydrogen and helium with 1 per cent heavier elements (metals), and can be in the form of clouds or diffuse regions.
Gas clouds include molecular clouds, cold neutral atomic hydrogen (\hi) or hot \hi~clouds, and diffuse gas can be either \hii~(ionized hydrogen) regions or hot intercloud medium.
Dust mostly contains silicate, graphite grains can be seen in dark clouds or galactic cirrus.
Emission lines from atoms or ions (i.e \hii~regions) in a hot gas, lines from molecules in cold clouds and 21~cm emission of \hi~are the main observational signatures of the gas in the ISM of galaxies.
Dust can be observed directly through far-infrared and sub-millimeter wavelength emission or indirectly through its extinction and attenuation effects (see Sec.~\ref{sec: extinction}).

Molecular clouds in the ISM are cold ($\sim10$ K) and dense ($ 50<n<500$ cm$^{-3}$); masses of molecular clouds range from a few to millions of solar masses~\citep{Bolato08}.
Density in the molecular clouds is not uniform; There are dense and colds clumps inside these clouds.
Since these clumps are ideal places to form stars, studying molecular clouds has an important role in understanding formation of stars
However, H$_2$ molecules, the main component of molecular clouds, have no permanent electric dipole moment which makes them difficult to detect.
The second dominant component, helium, is a mono-atomic gas and has the same problem as hydrogen, but these clouds also contain heavier elements such as carbon monoxide, hydrogen cyanide, water, ammonia and more than tens of others.
Carbon monoxide (CO) molecules are the third-most abundant constituent of molecular clouds.
In fact, most of our knowledge from molecular clouds comes from observing line emission of CO molecules, which {\bf due to their heavy weight, they have very low rotational state} and can be excited in the temperature of molecular clouds. %PB \bf needs clarification
Other heavier molecules have emission lines which are also detectable in the spectrum of clouds (specially galactic ones), but observing CO emission is the most common way to study the properties of molecular clouds i.e. their mass (see Sec.~\ref{sec: ismmap} for more details).

@@

\hii~regions are hot and low density regions that are mostly located in the disks of spiral galaxies.
High energy UV photons emitted by massive new born stars have sufficient energy to ionize their surrounding gas, and
~\halpha emission is the main observational feature of \hii~regions.
The temperature and density of these regions can be estimated by observing other recombination lines such as H$\beta$, and forbidden lines such as \sii, \oii, \oiii, and \nii. 
Forbidden lines are not ``forbidden", they only have much lower probability of occurring than the ``allowed" ones.
Optically bright \halpha emission from \hii~regions correlates with number of new massive stars in regions and can be used as a star formation tracer~\citep[e.g.][]{Kennicutt98b,Calzetti13}.
Studying \hii~regions provides valuable insight into star forming regions by providing information such as star formation rate, initial mass function (IMF), and distribution of ionizing stellar masses~\citep[][and references therein]{Azimlu11}.

Dust has an insignificant effect on the mass of the ISM, but it plays crucial roles in the ISM's evolution.
%The total gas mass of galaxies can be determined using optical depth in sub-mm waveband of dust emission. 
In spiral galaxies dust grains are located in cold regions ($\sim$30~K) and have a power-law distribution of size.
Source of dust thermal emission is from stars and shape of the continuum depends on size of the grain.
Mid-infrared emission from dust grains is mainly dominated by PAHs heated by evolved stellar population~\cite{Smith07a} or recently formed intermediate mass young stars~\cite{Peeters04}. 
Large grains that are either heated by light from star-forming regions or by the interstellar radiation field from total stellar population emit most of their light in far-infrared~\citep[e.g.][]{Calapa14, lu14}
Dust is the main source of extinction and reddening of starlight (See Sec.\ref{sec: extinction} for more information).

\subsection{Mapping the Interstellar Medium} 
\label{sec: ismmap}
Measuring the mass of gas in galaxies is a necessary step to know how much raw material is available for forming stars.
A map of the total gas mass in the ISM can be produced by direct observations of gas or using interstellar dust as a tracer. 
Neutral atomic and molecular hydrogen are the most common components of the ISM. 
Therefore, to produce a total gas mass map in galaxies, maps of these two components can be added together and multiplied by a constant factor to account for heavier elements which are mostly helium, which cannot be observed directly. 
Another way to do the mapping is to assume that the ratio of total gas to dust is constant across the galaxy, and convert dust observations to a map of total gas mass.

@@

The surface density of gas in the ISM of galaxies can be measured by direct observation of the neutral and molecular hydrogen.
This method can be promising if observational data with resolved molecular and atomic clouds are available.
However, given the state of the current technology, having the high resolution images of clouds for most of galaxies are not possible. 
This problem shows itself for distant galaxies more than nearby galaxies. 
As a result, using images of molecular and atomic cloud to measure surface density of gas in ISM is limited to telescopes resolution.

@@

\cite{Young91} described the relationship between the CO luminosity of a cloud and its mass. The CO luminosity of a cloud is:
\begin{equation}
L_{CO} = D^2 \int I_{\rm CO} d\Omega 
\end{equation}
where $D$ is the distance to the cloud and 
$I_{\mathrm CO}$ is the CO brightness temperature integrated over the line profile in KKms$^{-1}$.
It can be written as ${\int T_{\mathrm CO} dV}$ where $T_{\mathrm CO}$(k) is the peak brightness temperature in the CO line and $V$ is the line-width in Kms$^{-1}$.
For a uniform cloud with a radius $R$, the CO luminosity is given by:
 \begin{equation}
L_{\rm CO} = \pi R^2 T_{\rm CO} \Delta V
\end{equation}

Giant molecular clouds are self-gravitating systems~\citep[e.g.][]{Efstathiou83,Blitz99}.
Thus, using the virial theorem leads to calculating the mass of the cloud: 
 \begin{equation}
 \label{equ: vir}
 M_{cloud} = L_{\rm CO} \sqrt{\frac{4\rho}{3\pi G T_{\rm CO}}}
 \end{equation}
 where $\rho$ is the mass density of the cloud and $\sqrt{\frac{4\rho}{3\pi G T_{\rm CO}}}$ is called the conversion factor.
 Equ.~\ref{equ: vir} shows that the total mass of molecular clouds and the CO luminosity of the cloud are directly related~\citep{Young91}. 
 Since the dependency of $I_{\mathrm CO}$ to optical depth is negligible~\citep{Krumholz09}, total CO luminosity of the galaxies, can be used to measure the total H$_2$ mass of galaxies.
 The relation between CO emission and H$_2$ cloud mass is shown as
\begin{equation}
N_{\rm H_2}/\rm cm^{-2} = X_{\rm CO} \times I_{\rm CO}/{\rm K km s}^{-1}
\end{equation}
where X$_{\rm CO}$ is the conversion factor (also known as the X-factor).
The X-factor is different in each galaxy and sometimes is even different in regions within a galaxy due to differences in properties such as metallicity. 
Though assuming a constant conversion factor for galaxies like M82 and M31 can lead to accurate estimation of global molecular gas mass, in regions with low metallicity there are uncertainties~\citep{Bolato13}. 
Various groups are working on observations of different types of galaxies to measure the X-factor for them~\citep{Wilson95, Bosselli02, Bolato13}.

\begin{figure}
\label{fig: mco_ch}
\centering
\includegraphics[width=16cm]{../image_intro/mvirial_lco.pdf}
\caption{Relation between the virial mass and CO luminosity for the Milky Way (dots), M33 (open circles), M31 (triangles), and IC~10 (squares) clouds. Virial masses are measured from selected high spatial resolution CO observations. The extragalactic molecular clouds are very similar to those in the Milky Way. Adapted from~\cite{Young91}.}
\end{figure}

In order to empirically determine the relation between H$_2$ masses and CO luminosities, many observational attempts have been made on both Galactic and extragalactic scales. 
One of the most significant studies in this regard was done by~\cite{Solomon87}, who studied this relation over more than 273 clouds inside the Milky Way and found a strong correlation between the virial mass of molecular clouds and CO luminosity. 
In Local Group galaxies, several groups have measured size, line width, and CO luminosity of molecular clouds and investigated the relation between  their virial masses and CO emission in environment other than the Milky Way. 
Pioneering works in measuring the extragalactic conversion factor were done for M31 and M32~\citep[e.g.,][]{Wilson89, Wilson90}. 
Fig.~\ref{fig: mco_ch} shows the CO luminosity verses virial masses of molecular clouds in the Milky Way, M31, M33, and IC~10. 
The extragalactic molecular clouds are similar to those in the Milky Way. 
The conversion between the CO luminosity and H$_2$ masses is still a controversial topic~\citep[e.g.][]{Narayanan11, Bolato13, Sandstrom13}.
Problems regarding metallicity are not yet solved and it is still not clear whether the conversion factor is global or local. 
Extragalactic investigations were limited to nearby galaxies due to technical problems regarding resolution and sensitivity of the telescopes. 
To measure the clouds in distant galaxies, spatial resolution of maps must be better than 40 pc which is the typical size of a giant molecular cloud~\citep[e.g.][and refrences therein]{Young91,Bolato13}.

Atomic gas in galaxies are dominated by \hi~atoms, which are relatively easy to observe in 21-cm.
Assuming optically thin lines for \hi~emission, the intensity of the 21-cm emission is proportional to the density of the atomic hydrogen, $N_{H {\sc I}}$~(cm$^{-3}$), along the line-of-sight.
\begin{equation}
N_{H {\sc I}}  \propto \int T_{\mathrm B} dV
\end{equation}
where $T_{\mathrm B}$ is the temperature brightness in K and dV is in Kms$^{-1}$, with the integral over the line profile. 
These properties make the 21-cm line a very useful tool to study gas in the ISM and trace the large-scale distribution of galaxies in the universe (\hi is detectable in most spiral galaxies and some elliptical galaxies).
Although the 21-cm emission is the most reliable technique to map the ISM, the linear relationship between the intensity and the column density of the gas breaks down when the gas is optically thick~\citep{Braun09}.

@@

Studying the gas clouds in the ISM of distant galaxies by using direct methods is almost impossible and not practical, due to low spatial resolution of data.
\cite{Hildebran83} was the first to suggest that one way to estimate the mass of the gas in the ISM might be from the optical depth of the sub-mm continuum emission from the dust; continuum dust emission is generally optically thin. 
The Herschel Space Telescope \cite{Pilbratt10} measured the continuum dust emission from hundreds of galaxies\citep{Eales10, Oliver12}. 
This amount of observational data provides a unique opportunity to study the ISM of galaxies using dust emission. 
The observed FIR flux has almost no dependency on distance, thus, one of the advantages of using the dust emission as a tracer of the gas mass is that unlike the direct method, high spatial resolution is not necessary. 
The other important advantage is that this method solves the newly-found problem of the ``dark gas" in galaxies. 
Dark gas is a significant fraction of gas in galaxies which is traced by neither 21-cm emission nor CO emission~\citep{Abdo10}. 
As such it is very difficult to detect with telescopes, but an accurate gas to dust ratio can lead to an accurate estimate of dark gas mass in galaxies.
